Co-citations in context

### 2019-09-15 cocit_r_v3.tex
duplicate paras in Discu

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}. We also acknowledge the limitations of using citation counts to identify impactful publications. Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study in the context of co-citation may be merited. Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}

Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns. Further work might explore additional constraints on random assignment of citations to publications to better align benchmarks with citation practice. For example, proximity defined by co-author networks~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions. Another interesting but challenging direction would be to find ways to distinguish intra-disciplinary from cross-disciplinary novelty. \textcolor{blue}{In this respect, the related work of \citep{wang_bias_2017} is insightful with its use of empirical data and the observations made on novelty, quality, as well as dispersion and kinetics of accrued citations of articles.}

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. Such grouping, while appealing on account of its relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\citep{traag_louvain_2019, klavans_which_2017}}.  Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and appropriate consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.

>>>>

\textcolor{blue}{We note that journals are used as grouping units for articles in the three studies we discuss \citep{wang_bias_2017, uzzi_atypical_2013, boyack_vs_uzzi_2014} as well as this one. While we used keyword searches to identify sets of articles, we still relied on journal grouping to generate z-scores. Such grouping, while appealing on account of relative simplicity, obscures measurements of novel pairings at the article level. Journals are also of limited use in representing individual fields and repeating some of these studies using article clusters may be more informative~\cite{traag_louvain_2019, klavans_which_2017}. We also acknowledge the limitations of using citation counts to identify impactful publications. Various factors contribute to citations \citep{peters_determinants_1994, vieira_citations_2010} and further study of these in the context of co-citation may be merited. Overall, evaluation in context~\citep{hicks_bibliometrics:_2015} and further consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.}
